Flatiron cleaning

### 2021-10-27 Rmd/rdi analysis.Rmd
Adding cleanup for cycle number and more

Also height, weight, bsa, creatinine is cleaned and ready. Creatinine minimum is now capped at 0.7 and not 0.8.  
Creatinine clearance maximum is capped at 125.

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = first(episodedate)) %>% 
  mutate(lineenddate_new = last(episodedate)) %>% 
  ungroup()

@@

`r emo::ji("question_mark")` **Are we keeping the patients who had Neo + surgery without Adjuvant?**

@@

Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

  mutate(remove_linename_other = case_when(
    linenumber_new == 1 &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
                                                                         ~ "remove",
    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      str_detect(linename, 
                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
                                                                         ~ "remove",
    linenumber_new == 2 &
      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
    TRUE                                           ~ NA_character_
  )) %>% 
  arrange(patientid, episodedate)

remove_linename_other <- remove_linename_other %>% 
  filter(remove_linename_other == "remove") %>% 
  distinct(patientid, .keep_all = T)

remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with other linename
  filter(!str_detect(patientid, remove_linename_other)) %>% 
  arrange(patientid, episodedate)
```

@@

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, drugname, episodedate, line_duration, 
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, linenumber_adj) %>% 
  filter(line_duration < 30)
```

<!-- Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):   -->
<!-- In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2 -->

<!-- <br> -->

<!-- | linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             1                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  | happened |             2                  | platin   |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
<!-- |             1                  |          |             2                  | taxel    |   -->
<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->

<!-- <br> -->

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_increment) %>% 
  group_by(patientid, linenumber_new) %>%
  # mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
```

@@

### If we keep as is, the
## **Number of patients in final dataset is `r Treatment %>% distinct(patientid) %>% nrow()`**

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug <= 1                ~ "correct",
    # mean_RDI_per_drug == 1                 ~ "perfect",
    # mean_RDI_per_drug > 1 &
    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("correct", #"perfect", #"higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>
<br>

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

@@

## Missingness
Here some representation of missingness in our data:  
- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.   
- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
```{r}
library(naniar)
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat",

           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",

           "hrd_tissue", "gis_tissue")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>

>>>>

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = first(episodedate)) %>% 
  mutate(lineenddate_new = last(episodedate)) %>% 
  ungroup() %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

@@

`r emo::ji("check")`

@@

Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo

therapy_line <- therapy_line %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

@@

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, surgerydate, episodedate, line_duration, drugname,
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, linenumber_adj) %>% 
  filter(line_duration < 30) %>% 
  arrange(line_duration, patientid, episodedate)
```

@@

  # group_by(patientid, linenumber_new, cycle_inc) %>%
  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
  arrange(patientid, episodedate, cycle_increment) %>% 
  group_by(patientid, linenumber_new) %>%
  # mutate(cycle_increment = cycle_inc) %>% 
  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
  mutate(is_dose_dense = row_number(cycle_increment),
         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
  group_by(patientid) %>% 
  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
  fill(total_cycle_increment, .direction = "downup") %>% 
  # cycle date
  group_by(patientid, linenumber_new, cycle_increment) %>% 
  mutate(cycle_start_date = min(episodedate)) %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate,
  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  ungroup()
therapy_cycle %>% distinct(patientid) %>% nrow()

```

```{r remove more than 9 cycle patients}
too_much_cycle <- therapy_cycle %>% 
  filter(
    (therapy == "Upfront Surgery" & total_cycle_increment > 9) |
      (therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant" & total_cycle_increment > 9)
  ) %>%
  distinct(patientid)
too_much_cycle <- paste(too_much_cycle$patientid, collapse = "|")

therapy_cycle <- therapy_cycle %>% 
  # remove these patients who switched C > C 
  filter(!str_detect(patientid, too_much_cycle))
therapy_cycle %>% distinct(patientid) %>% nrow()
```

@@

### **Number of patients : `r Treatment %>% distinct(patientid) %>% nrow()`**

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug <= 1                ~ "correct",
    # mean_RDI_per_drug == 1                 ~ "perfect",
    # mean_RDI_per_drug > 1 &
    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("correct", #"perfect", #"higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>

# Remove patients who don't have any RDI
```{r remove no RDI patients}
no_rdi <- Frontline %>% 
  arrange(RDI_grp) %>% 
  distinct(patientid, .keep_all = TRUE) %>% select(patientid, RDI_grp) %>% 
  filter(is.na(RDI_grp))

no_rdi <- paste(no_rdi$patientid, collapse = "|")

Frontline <- Frontline %>% 
  # remove these patients who switched C > C 
  filter(!str_detect(patientid, no_rdi))
Frontline %>% distinct(patientid) %>% nrow()
```
<br>

### If we keep as is, the
## **Number of patients in final dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(cycle_increment)) %>% 
  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```

Number of Adjuvant line in patients with upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))

Treatment %>% 
  filter(therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
  arrange(desc(total_cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(total_cycle_increment) %>% 
  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

@@

## Missingness
Here some representation of missingness in our data:  
- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.   
- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
```{r}
library(naniar)

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat")) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

# # OS by brca1_tumor
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by brca2_tumor
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by brca_tumor
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by brca1_g
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))
# 
# # OS by brca2_g
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
